---
title: "delivery time experiment"
author: "Yulong Gong, Tzuhua Huang, Chenzhi Pan, Muyan Xie, Yichi Zhang, Yangyang Zhou"
output:
  pdf_document: default
  html_document: default
---
# Introduction

The COVID-19 pandemic challenged our life in many aspects,but some industries grew quickly during this period, such as fresh delivery services. As many pieces of research have shown, in this fast-paced society, people value the speed of delivery service. According to Resendes (2020), 31% of customers use delivery service at least twice a week. 33% of customers are willing to pay money in exchange for fast delivery.

For this project, we would like to dive into the food delivery service industry. We’d like to take the standpoint of the third-party food delivery service platforms, such as Uber Eats, Chowbus, DoorDash, etc., which connect the restaurants and consumers. We want to analyze when everything holds constant, how the food delivery time interval will affect consumer’s willingness to place an order. 

We wish our results could help us have a better understanding of the influence of wait time on whether a consumer would choose a service or not, which could be helpful in our career. Also, we wish our result to develop a win-win relationship between consumers and service platforms by helping platforms gain more profits and consumers have better user experience.

# Hypothesis and implications
We assume that the more precise the delivery time interval is, the more willingly a customer will place an order. In this case, the platform should improve the accuracy of estimated delivery time or optimize the delivery time to a narrower interval.


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(scipen=1, digits=3)

library(data.table)
library(tidyverse)
library(lfe)
library(fixest)
library(lubridate)
library(stargazer)
library(modelsummary)
library(kableExtra)
library(ggplot2)
treat <- fread('Treatment.csv')
control <- fread('Control.csv')
# treatment indicator
treat[, any_treatment := 1]
control[, any_treatment := 0]
summary(control)
# combine tables
data <- rbind(treat, control,fill=TRUE)
# order frequency 
data[,frequency := ifelse((Q6 ==  '> 3 times a week' | data$Q6 == '2-3 times a week'),1,0)]
# work from home 
data[, wfh := ifelse(Q4 == 'Yes', 1, 0)]
# student 
data[, student := ifelse(Q3 == 'Yes', 1, 0)]
# membership
data[, member := ifelse(Q9 == 'None of the above', 0, 1)]
# favor cuisine is chinese or not
data[, chinese := ifelse(Q7 == 'Chinese',1,0)]

# Select all rows with frequency and favor cuisine input
keep <- which(data$Q6 != '')
data <- data[keep]
```

# Method

**Questionnaire Design**
There are three steps for designing the questionnaire. Firstly, demographic information are collected. We would like to know if the participant is a student or an employee for an organization and if he/she is working/studying from home.

Second, we asked the participants' experience of using food delivery service, as recommended by K.Foreit and J.Foreit(2004) in their paper. To be specific, the frequency of using food delivery services and whether the individual is an existing user for any existing platforms. We also collected the personal preference on food categories.

Next, we simulated two interfaces. For the treated group, the participant would see the ordering page with the delivery time interval of 10 minutes (e.g., Your food will be delivered between 7:00 pm -7:10 pm); while the control group will see the same restaurant as the treatment group. The only difference would be the delivery time interval is greater than 30 minutes (e.g., Your food will be delivered between 7:00 pm – 7:40 pm). We also provided the options across different food categories, and we chose the same image representation so we could eliminate the impact of food categories on participants' decision-making as much as possible. In each question, the participant should decide if he/she would like to place an order based on the picture and the information we provided. 

Finally, we asked the individual to provide the reasons if he/she chose unwilling to place an order in the previous questions. We would like to collect the potential reasons that might lead to participants' decisions and examine if the results could support our hypothesis.

```{r}
# variable questions table 
questions = data.table(
  Variables = c("'member'","'student'","'wfh'","'frequency'","'chinese'"),
  Question = c("Are you a member of any food delivery platforms?","Are you a student?","Do you currently work/study from home?","How often do you order delivery?","What's your favorite cuisine when you order takeout/delivery?")
)
kbl(questions)
```


**Participants**

To decide which participants would be in the treatment or control group, we decided to use the built-in function in Qualtrics, a survey design platform. By setting automatic randomization, the questionnaire would randomly present one of the interfaces to the individual with 50% chance seeing the treatment questions. By appropriately designing the randomizer in the questionnaire, we were able to randomize everyone into the control or treatment group in an attempt to avoid selection bias in the study.

To recruit the participants, we distributed our questionnaires in two ways. Firstly, we distributed it by posting messages in the ‘QuestromMSBA21’ Slack channel. Secondly, we also distributed through our social networking.  Finally, we had a total of 91 respondents from under 19 to 39. Additionally, 54 identify as female, and 36 identify as male.


**Pre-Experiment Randomization/Balance Check**

We run three regressions for balance check. The results show that we randomized our variables well. None of the variables are statistically significant at 95% confidence level. Therefore, we can conclude that there's no significant difference between treatment and control groups among whether the participant is working from home, whether the participant is a student, and whether the participant is a member of any food delivery platform. None of these characteristics made participants more likely to be in the treatment group.
```{r, warning=FALSE}
# work from home check
sample <- lm(wfh ~ any_treatment, data)
# student check
sample1 <- lm(student ~ any_treatment, data)
# membership check
sample2 <- lm(member ~ any_treatment, data)
# frequency check
sample3 <- lm(frequency ~ any_treatment, data)
# Chinese food check
sample4 <- lm(chinese ~ any_treatment, data)

# combine together
stargazer(sample, sample1, sample2, sample3, sample4, type = 'text')
```


**EDA**
From the below graph we notice that the majority of our participants ordered Chinese food.
```{r, warining=FALSE}
#Cuisine distribution
cuisine <- ggplot(data = data,aes(x=Q7,fill=Q7))+
  geom_histogram(stat = 'count')+
  ggtitle('Cuisine Distribution')+
  ylab('Count') + xlab('Cuisines')
cuisine
```
From the order frequency chart we find out that most of our participants order food from delivery apps more than 2 times a week.
```{r, warning=FALSE}
#Order frequency
order <- ggplot(data = data,aes(x=Q6,fill=Q6))+
  geom_histogram(stat = 'count')+
  ggtitle('Order Frequency Distribution')+
  ylab('Count') + xlab('Order frequencies') + coord_flip()
order
```

```{r}
head(data)
```

# Data Analysis

We would like to perform a series of regressions to analyze the results of our experiment. First of all, we calculated average treatment effect for our experiment which is whether the range of delivery time provided affect the probability of ordering. Since our experiment included different types of cuisine trying to minimize differences on personal flavors, we compute the average or the probability that they will order food from five pictures we provided. 
Based on the result below, we observe that, in general, participants in treatment group are 13% more likely to order delivery than those in control groups. This result suggests that users are more likely to order food with small range of delivery time. In addition, below table suggests our result is statistically significant at 95% confidence level. 
```{r}
reg1 <- feols(avg_score ~ any_treatment, data = data,se="white")
etable(reg1)
```
Then, we added those variables from balance check as controls. However, they did not reduce variance in estimation. 
```{r}
reg2 <- feols(avg_score ~ any_treatment + wfh + student + member, data = data, se='white')
etable(reg2)
```
Then, we dive deeper into the food categories. We would like to explore how does the delivery time range affect people's ordering decisions by different food categories. From the regressions below, we use all 91 participants data. We can see that for Fast Food and Italian Food (which is a pizzeria in our survey), the difference between treatment group (shorter delivery time range) and control group (longer delivery time range) is statistically significant at 90% confidence level. The result implies that people who order from a fast food restaurant or a pizzeria are more time sensitive. They want their delivery time range as short as possible. 
```{r}
#For all surveys
##===============================================MU YAN ====================================================
reg3 <- feols(Japanese ~ any_treatment, data = data, se='white')
reg4 <- feols(American ~ any_treatment, data = data, se='white')
reg5 <- feols(Fast ~ any_treatment, data = data, se='white')
reg6 <- feols(Chinese ~ any_treatment, data = data, se='white')
reg7 <- feols(Italian ~ any_treatment, data = data, se='white')
etable(reg3, reg4, reg5, reg6, reg7)
```

# Chinese vs non-Chinese
From the summary below we could observe that , there is a small differences on probability of ordering deliver services between users who favor Chinese and not. In addition, users who favor ordering Chinese cuisine are slight more in favor of short delivery time interval estimate.
```{r}
reg8 <- feols(avg_score~any_treatment*chinese,data,se='white')
etable(reg1,reg8)
```
```{r}
cate_chinese_1 <- mean(data[chinese == 1& any_treatment == 1, avg_score])-mean(data[chinese == 1& any_treatment == 0, avg_score])
cate_chinese_0 <- mean(data[chinese == 0& any_treatment == 1, avg_score])-mean(data[chinese == 0& any_treatment == 0, avg_score])
cat(cate_chinese_1,cate_chinese_0)
```
 

# Order Frequency
Then we want to take a close look at people who order food more frequently. From the regression we notice that the difference between treatment group and control group for Chinese Food become statistically significant. One reasonable explanation would be part of our participants located in China, and delivery time range in China is more precise. Therefore, those part of people are more likely to order when the delivery time range is short. People who ordered food frequently are very time sensitive. They do not want to wait for a long time.
```{r}
#For people with higher order frequency
reg9 <- feols(avg_score~any_treatment*frequency,data,se='white')
etable(reg1,reg9)
```
```{r}
cate_frequency_1 <- mean(data[frequency == 1& any_treatment == 1, avg_score])-mean(data[frequency == 1& any_treatment == 0, avg_score])
cate_frequency_0 <- mean(data[frequency == 0& any_treatment == 1, avg_score])-mean(data[frequency == 0& any_treatment == 0, avg_score])
cat(cate_frequency_1,cate_frequency_0)
```

# Conclusion
Based on the above summary, we can conclude that the average treatment effect varies by users' previous order frequency. Users who had high previous order frequency tended to pay more attention to the food delivery time range. Those users were 16.4% more likely to place an order with a short range of delivery time than with a relatively long range. Users had low previous order frequency, however, didn't really seem to take the range of delivery time into account. 

# Limitation
Even though we tried to be as comprehensive as we could, this project still has some limitations.

To start with,  the questionnaire did not cover all possible types of diets such to be specific,  we did not consider whether the respondent is a vegetarian or not. 

The combination of all order placement questions may lead to confusion which could fail to make respondents consider each question individually, and they may even didn’t notice the food type differences. Even worse,  the person may just pick favorite food cuisines and ignore the delivery time we set on purpose.

Though this sampling method was efficient, some biases emerged when we recruited only people we know. First, the sample can't be representative of people of all ages. Second, we have a disproportionate number of participants who are students since we approached a lot of classmates. This might cause the external validity of our results and makes it difficult to apply our findings to a larger population. 

# Further research
During our data analysis process, we realize that qualtrics automatically collect geographical information, so if we can distribute our samples on a larger scale, we may be able to check whether there are block-wise characteristics.
Furthermore, we could include some questions about the average cost per order to check whether the longer individual waits, the more she/he is likely to spend. 

# References:
Foreit, K. G., & Foreit, J. R. (2004). Willingness to pay surveys for setting prices for reproductive health products and services a user’s manual.

Lock, S. (2020). Food delivery services: market share U.S. 2018-2022. Statista. Retrieved from
https://www.statista.com/statistics/1080860/market-share-us-food-delivery-companies/

Parry, T. (2016, Sept 13). Delivery time influences 87% of online shoppers’ purchase decisions, Multichannel Merchant, retrieved fromhttps://multichannelmerchant.com/must-reads/delivery-time-influences-87-online-shoppers-purchase-decisions/ 

Resendes,.S (2020). 26 Online ordering statistics every restaurateur should know in 2020. Upserve. Retrieved from https://upserve.com/restaurant-insider/online-ordering-statistics/








